Considering scale in multilayer animal social networks

### 2020-06-14 paper/manuscript.Rmd
nobs results

<!-- TODO: reduce to this version -->
As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength was consistently weak in summer layers but varied in winter layers at
low number of observations, becoming stable at ~75 observations (Figure
\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
winter layers increased between approximately 10  and 100  observations,
remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
coarse land cover resolution (Figure \@ref(fig:lcres)), low numbers of
observations were not sufficient for capturing individuals in all contexts and
therefore layer similarity could not be calculated below ~30 observations for
forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
similarity was not possible to calculate for forage layers because there were no
connected individuals in summer forage. Once sufficient observations were
obtained, layer similarity showed some variability with increasing numbers of
observations for forest and was relatively stable in open layers. Connective
redundancy increased dramatically between ~10 and ~50 observations before
stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
Given the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.

<!-- TODO: I'm not sure this is relevant since this is the main way it
is already done, can we make this thought more relevant to picking scales or
multilayer networks in general? I think it's important for building robust
networks -->

>>>>

<!-- TODO: reduce to this version -->
As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize. Graph
strength across individuals in all three habitat layers was highly variable at low number of observations and stabilized after ~100 observations (Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat layers with increasing number of observations (Figure \@ref(fig:nobs) B). Similarly, multidegree for all individuals increased quickly between 10 and 100 observations, and continued to increase until 1000 observations (Figure \@ref(fig:nobs) C). Given the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.

<!-- sufficient observations is essential for capturing reliable networ -->
